---
title: "Code Check"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(beemixtox)
```


It feels strange that in Figure 4b, the different subsets would produce different sets of driver substances and their rankings. 

Figure 4b. Needs revision to ensure all is correct. If you compare “Figure4b-Chronic-Current_Use.png" and “Figure4b-Chronic-Excluded_Metals.png",  I see there are some chemicals missing that should appear at the top of the ranking in “Figure4b-Chronic-Excluded_Metals.png", Such as Ibuprofen, Erythromycin, diclofenac, and Ethinylstradiol. See what part of the dataset you are restricting when limiting to 40 (if the head or the tail).


- For driver substances, for example, Ibuprofen . 

```{r}
"Ibuprofen" %in% chemclass$Substance

chemclass %>% filter(Substance=="Ibuprofen")
Ibuprofen <- casdata %>% filter(Substance=="Ibuprofen")
```

- Excluded Metals

```{r}
table(driverdata$Exclusion.CAS)


driver_Ibuprofen <- driverdata %>% filter(Exclusion.CAS=="Excluded_Metals" & LOQ.type=="LOQ.T0" & test=="Chronic" & CAS=="15687271")
table(driver_Ibuprofen$Component)
Data.AggBySiteID.3a <-  preprocessWaterbase(Data.AggBySiteID.2,chemclass,LOQ.type = "LOQ.T0",
                                                Data.SSD.1 = Data.SSD.1,Exclusion.CAS= "Excluded_Metals",
                                                HU=F,PAF=F)

driver_Ibuprofen <-driver_Ibuprofen %>% left_join(Data.AggBySiteID.3a)%>% mutate(HC05.Chronic= 10^qnorm(0.05,Ibuprofen$SSDLOG10.Mu.chronic.NOEC, Ibuprofen$SSDLOG10.Sigma.chronic.NOEC)) %>% mutate(HQ.Chronic=resultMeanValue/HC05.Chronic)
plot(density(driver_Ibuprofen$HQ.Chronic))
skimr::skim(driver_Ibuprofen$HQ.Chronic)
quantile(driver_Ibuprofen$HQ.Chronic,c(0,0.25,0.5,0.75,0.95,1))


HQdata <- getHQData_Chronic(Data.AggBySiteID.2,chemclass=chemclass,Data.SSD.1=Data.SSD.1,LOQ.type= c("LOQ.T0"),driverdata,Exclusion.CAS="Excluded_Metals")
sumCAS <- HQdata %>% mutate(test="Chronic") %>%group_by(LOQ.type,test)%>%mutate(nSample=length(unique(Site.Year))) %>% group_by(LOQ.type,test,CAS,nSample) %>%nest() %>% mutate(nappear=purrr::map(data,nrow),QI=purrr::map(data,function(df) quantile(df$HQ.Chronic,c(0.25,0.5,0.75,0.95,1))))%>% unnest(cols=c(nappear,QI))%>% mutate(freq=nappear/nSample ) %>% select(-data) %>% mutate(Quantile=c("25%","50%","75%","95%","100%"))%>% group_by(LOQ.type,test,CAS)%>% mutate(q95=QI[Quantile=="95%"])%>% filter(q95>0.01)%>% group_by(LOQ.type,test)%>%nest()%>%mutate(data=purrr::map(data,function(df){df <- df %>% group_by(CAS,q95) %>% nest()
    df <- df[order(df$q95,decreasing = T),]
    df <- df %>% add_column(x=1:nrow(df))
    df <- df %>% unnest(cols=c(data))
    return(df)
  }))%>%unnest(cols = c(data))%>%ungroup #
sumCAS %>% filter(CAS=="15687271")   
```




```{r}
driver_Ibuprofen <- driverdata %>% filter(Exclusion.CAS=="Current_Use" & LOQ.type=="LOQ.T0" & test=="Chronic" & CAS=="15687271")
table(driver_Ibuprofen$Component)
Data.AggBySiteID.3a <-  preprocessWaterbase(Data.AggBySiteID.2,chemclass,LOQ.type = "LOQ.T0",
                                                Data.SSD.1 = Data.SSD.1,Exclusion.CAS= "Current_Use",
                                                HU=F,PAF=F)

driver_Ibuprofen <-driver_Ibuprofen %>% left_join(Data.AggBySiteID.3a)%>% mutate(HC05.Chronic= 10^qnorm(0.05,Ibuprofen$SSDLOG10.Mu.chronic.NOEC, Ibuprofen$SSDLOG10.Sigma.chronic.NOEC)) %>% mutate(HQ.Chronic=resultMeanValue/HC05.Chronic)
plot(density(driver_Ibuprofen$HQ.Chronic))
skimr::skim(driver_Ibuprofen$HQ.Chronic)
quantile(driver_Ibuprofen$HQ.Chronic,c(0,0.25,0.5,0.75,0.95,1))


HQdata <- getHQData_Chronic(Data.AggBySiteID.2,chemclass=chemclass,Data.SSD.1=Data.SSD.1,LOQ.type= c("LOQ.T0"),driverdata,Exclusion.CAS="Current_Use")
sumCAS <- HQdata %>% mutate(test="Chronic") %>%group_by(LOQ.type,test)%>%mutate(nSample=length(unique(Site.Year))) %>% group_by(LOQ.type,test,CAS,nSample) %>%nest() %>% mutate(nappear=purrr::map(data,nrow),QI=purrr::map(data,function(df) quantile(df$HQ.Chronic,c(0.25,0.5,0.75,0.95,1))))%>% unnest(cols=c(nappear,QI))%>% mutate(freq=nappear/nSample ) %>% select(-data) %>% mutate(Quantile=c("25%","50%","75%","95%","100%"))%>% group_by(LOQ.type,test,CAS)%>% mutate(q95=QI[Quantile=="95%"])%>% filter(q95>0.01)%>% group_by(LOQ.type,test)%>%nest()%>%mutate(data=purrr::map(data,function(df){df <- df %>% group_by(CAS,q95) %>% nest()
    df <- df[order(df$q95),]
    df <- df %>% add_column(x=1:nrow(df))
    df <- df %>% unnest(cols=c(data))
    return(df)
  }))%>%unnest(cols = c(data))%>%ungroup #
sumCAS %>% filter(CAS=="15687271")   

# # A tibble: 5 x 10
#   LOQ.type test    CAS        q95 nSample nappear    QI  freq Quantile     x
#   <chr>    <chr>   <chr>    <dbl>   <int>   <int> <dbl> <dbl> <chr>    <int>
# 1 LOQ.T0   Chronic 15687271  1.15    5506     903 0.101 0.164 25%         19
# 2 LOQ.T0   Chronic 15687271  1.15    5506     903 0.182 0.164 50%         19
# 3 LOQ.T0   Chronic 15687271  1.15    5506     903 0.339 0.164 75%         19
# 4 LOQ.T0   Chronic 15687271  1.15    5506     903 1.15  0.164 95%         19
# 5 LOQ.T0   Chronic 15687271  1.15    5506     903 5.69  0.164 100%        19
# > quantile(driver_Ibuprofen$HQ.Chronic,c(0,0.25,0.5,0.75,0.95,1))
#         0%        25%        50%        75%        95%       100% 
# 0.08703508 0.40400597 0.67887364 1.10215788 1.80128894 5.68991848 
```

