---
title: "DropAcute"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(beemixtox)
```



```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval=T,
  fig.width = 12,
  fig.height = 10
)
library(pander)
panderOptions("table.split.table",Inf)
```




## Figures for the Manuscript


```{r}
library(beemixtox)
library(quantreg)
library(tidyverse)
data("Data.AggBySiteID.2")
tmp1 <- Data.AggBySiteID.2 %>% group_by(Site.Year) %>% summarise(N=length(Site.Year)) %>% mutate(n1=mean(N))
data("Data.SSD")
data("chemclass")
CAS.SSD = unique(Data.AggBySiteID.2$CAS)[unique(Data.AggBySiteID.2$CAS)%in%as.character(unique(Data.SSD$CAS.))]
Data.SSD.1 = Data.SSD[Data.SSD$CAS.%in%CAS.SSD,]; Data.SSD.1 = droplevels(Data.SSD.1)

```

### Figure 1

Figure 1. log10(HI)-MCR Plots. Faceted plot (2x3). 

Chronic, same for Acute (for SM Materials) 

LOQ.type = c("LOQ.T0", "LOQ.T1") 

Exclusion.CAS = c("Excluded_None", "Excluded_Metals", "Current_Use") 

**Note that 1808 site.year has HI of 0, around 15.5 %**




```{r}
Res <- getResData(Data.AggBySiteID.2,chemclass,LOQ.type = c("LOQ.T0","LOQ.T1"),
            Exclusion.CAS = c("Excluded_None","Refined_Metals_PAH","Excluded_Metals","Current_Use"),Data.SSD.1)

```

```{r}
cutoff <- 5
Res <- Res%>%filter(Nmeasured>cutoff)
```


- save the table first before the plot

Table 1. CEFIC-MIAT Table 

- Include only AF 1 (Do we want to include other Afs?) 
- Chronic, same for Acute (for SM Materials) 
- LOQ.type = c("LOQ.T0", "LOQ.T1") 
- Exclusion.CAS = c("Excluded_None", "Excluded_Metals", "Current_Use") 
- Generate identical Table for Acute for SM. 

```{r}
N_CAS_Site_tmp <- Res %>% group_by(LOQ.type,Exclusion.CAS) %>% summarise(N.Site=length(unique(monitoringSiteIdentifier)),N.Sample=length(monitoringSiteIdentifier)) %>% mutate(Exclusion.CAS=factor(Exclusion.CAS,levels=c("Excluded_None","Refined_Metals_PAH","Excluded_Metals","Current_Use")))
table_chronic <- Res%>% group_by(LOQ.type,Exclusion.CAS,Group_AF1_Chronic) %>% summarise(N=length(monitoringSiteIdentifier))%>% ungroup %>% left_join(N_CAS_Site_tmp[,c("LOQ.type","Exclusion.CAS","N.Sample")])%>% mutate(Perc=N/N.Sample*100)
```


```{r}
if(interactive()){
  write.csv(table_chronic,file="inst/manuscript_cutoff_5measured/table_chronic_5measured.csv")
}

```


```{r}
table_chronic%>% knitr::kable(.,format = "html")%>%kableExtra::collapse_rows(.)
```


```{r}
table_acute <- Res%>% group_by(LOQ.type,Exclusion.CAS,Group_AF1_Acute) %>% summarise(N=length(monitoringSiteIdentifier))%>% ungroup %>% left_join(N_CAS_Site_tmp[,c("LOQ.type","Exclusion.CAS","N.Sample")])%>% mutate(Perc=N/N.Sample*100)
if(interactive()){
  write.csv(table_acute,file="inst/manuscript_cutoff_5measured/table_acute_5measured.csv")
}
```

```{r}
table_acute%>% knitr::kable(.,format = "html")%>%kableExtra::collapse_rows(.)
```


## Figure 1

```{r}
recting <- rbind(data.frame(xmin=-Inf,xmax=1,ymin=-Inf,ymax=Inf,col="green"),
                 data.frame(xmin=1,xmax=Inf,ymin=0,ymax=2,col="red"),
                  data.frame(xmin=1,xmax=Inf,ymin=2,ymax=Inf,col="yellow"))
```



```{r}
sum(Res$HI_Acute==0 & Res$Exclusion.CAS=="Excluded_None" & Res$LOQ.type=="LOQ.T0")
sum(Res$HI_Acute==0 & Res$Exclusion.CAS=="Excluded_None" & Res$LOQ.type=="LOQ.T1")

df <- data.frame(x=1e-6,y=9)

N_CAS_Site <- Res %>% group_by(LOQ.type,Exclusion.CAS) %>% summarise(N.Site=length(unique(monitoringSiteIdentifier)),N.Sample=length(monitoringSiteIdentifier)) %>% mutate(Exclusion.CAS=factor(Exclusion.CAS,levels=c("Excluded_None","Refined_Metals_PAH","Excluded_Metals","Current_Use")))
N.CAS <- sapply(c("Excluded_None","Refined_Metals_PAH","Excluded_Metals","Current_Use"),function(x)getNcas(x,chemclass))
N_CAS_Site$N.CAS <- rep(N.CAS[unique(N_CAS_Site$Exclusion.CAS)],2)
N_CAS_Site <- data.frame(df,N_CAS_Site)

Nclass <- Res %>% group_by(LOQ.type,Exclusion.CAS,Group_AF1_Acute) %>% summarise(N=length(monitoringSiteIdentifier))%>% left_join(N_CAS_Site[,c("LOQ.type","Exclusion.CAS","N.Sample")])%>% mutate(Perc=N/N.Sample*100)

Nclass1 <- Nclass %>% filter(Group_AF1_Acute=="IIIA" | Group_AF1_Acute =="IIIB")%>% group_by(LOQ.type,Exclusion.CAS) %>% summarise(Perc=sum(Perc)) %>% mutate(Group="III")

Nclass <- rbind(Nclass1,Nclass[,c("LOQ.type","Exclusion.CAS","Perc","Group_AF1_Acute")]%>%rename(Group=Group_AF1_Acute)%>%filter(Group=="I"|Group=="II"))

df1 <- data.frame(x=1e-6,y=7,Label="No concern",Group="II")
df1 <- rbind(df1,data.frame(x=20,y=5,Label="Single Substance Risk",Group="I"))
df1 <- rbind(df1,data.frame(x=5,y=10,Label="Multiple Chemicals Risk",Group="III"))
Nclass <- Nclass %>% left_join(df1)
```



```{r}
#ggplot(Res,aes(x=log10(HI_Acute),y=MCR.HC50.Acute.EC50))+geom_point()+geom_text(data=df,aes(x=x,y=y),label=paste0("N.Site = ",10,"\nN.CAS = ",5))+facet_grid(LOQ.type~Exclusion.CAS)
Res_1 <- Res %>% filter(LOQ.type=="LOQ.T0" & Exclusion.CAS != "Excluded_None") %>% droplevels(.)
N_CAS_Site_1 <- N_CAS_Site%>% filter(LOQ.type=="LOQ.T0" & Exclusion.CAS != "Excluded_None")%>% droplevels(.)
Nclass_1 <- Nclass%>% filter(LOQ.type=="LOQ.T0" & Exclusion.CAS != "Excluded_None")%>% droplevels(.)

ggplot(Res_1,aes(x=HI_Acute,y=MCR.HC50.Acute.EC50))+geom_point(aes(col=Group_AF1_Acute))+geom_text(data=N_CAS_Site_1,aes(x=x,y=y,label=paste0("N.Site = ",N.Site,"\nN.CAS = ",N.CAS,"\nN.Sample = ",N.Sample)))+geom_text(data=Nclass_1,aes(x=x,y=y,label=paste0(Group,"\n",formatC(Perc,digits = 2,format="f"),"%")),vjust="inward") +scale_x_log10()+geom_vline(xintercept = 1,col="blue")+geom_hline(yintercept = 2,col="blue")+facet_grid(LOQ.type~Exclusion.CAS,scale="free")+ annotate("rect", xmin = 1e-10, xmax = 1, ymin = recting[1,3], ymax = recting[1,4],fill="yellow",alpha=0.2)+geom_line(data=data.frame(x=seq(1,10,length=100),y=seq(1,10,length=100)),aes(x=x,y=y),col="blue")+theme(legend.position = "bottom")
# geom_rect(data=recting,aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax,fill=col))
# ggplot(data.frame(x=1:10,y=1:10),aes(x=x,y=y))+geom_point()+scale_x_log10()+ geom_line() 
if(interactive()){
  ggsave("inst/manuscript_cutoff_5measured/Figure1-Acute.png",width = 15,height=8,dpi=300)
}
```


- here we want to combine the acute and chronic results

```{r}
N_CAS_Site_Acute <- N_CAS_Site_1 %>% mutate(test="Acute")
Nclass_Acute <- Nclass_1 %>% mutate(test="Acute")
Res_Acute <- Res_1 %>% mutate(MCR=MCR.HC50.Acute.EC50,HI=HI_Acute,Group_AF1=Group_AF1_Acute)%>% mutate(test="Acute")

```


```{r}
N_CAS_Site$y <- 8


Nclass <- Res %>% group_by(LOQ.type,Exclusion.CAS,Group_AF1_Chronic) %>% summarise(N=length(monitoringSiteIdentifier))%>% left_join(N_CAS_Site[,c("LOQ.type","Exclusion.CAS","N.Sample")])%>% mutate(Perc=N/N.Sample*100)
Nclass1 <- Nclass %>% filter(Group_AF1_Chronic=="IIIA" | Group_AF1_Chronic =="IIIB")%>% group_by(LOQ.type,Exclusion.CAS) %>% summarise(Perc=sum(Perc)) %>% mutate(Group="III")

Nclass <- rbind(Nclass1,Nclass[,c("LOQ.type","Exclusion.CAS","Perc","Group_AF1_Chronic")]%>%rename(Group=Group_AF1_Chronic)%>%filter(Group=="I"|Group=="II"))

df1 <- data.frame(x=1e-6,y=4,Label="No concern",Group="II")
df1 <- rbind(df1,data.frame(x=50,y=5,Label="Single Substance Risk",Group="I"))
df1 <- rbind(df1,data.frame(x=5,y=9,Label="Multiple Chemicals Risk",Group="III"))
Nclass <- Nclass %>% left_join(df1)
Nclass_1 <- Nclass%>% filter(LOQ.type=="LOQ.T0" & Exclusion.CAS != "Excluded_None")%>% droplevels(.)

p1_ave <- ggplot(Res_1,aes(x=HI_Chronic,y=MCR.HC05.Chronic.NOEC))+geom_point(aes(col=Group_AF1_Chronic))+geom_text(data=N_CAS_Site_1,aes(x=x,y=y,label=paste0("N.Site = ",N.Site,"\nN.CAS = ",N.CAS,"\nN.Sample = ",N.Sample)))+geom_text(data=Nclass_1,aes(x=x,y=y,label=paste0(Group,"\n",formatC(Perc,digits = 2,format="f"),"%")),vjust="inward")  +scale_x_log10()+geom_vline(xintercept = 1)+facet_grid(LOQ.type~Exclusion.CAS,scale="free")+ annotate("rect", xmin = 1e-10, xmax = 1, ymin = recting[1,3], ymax = recting[1,4],fill="yellow",alpha=0.2)+geom_line(data=data.frame(x=seq(1,10,length=100),y=seq(1,10,length=100)),aes(x=x,y=y))+scale_y_continuous(limits=(c(1,10)),expand = c(0,0))+theme(legend.position = "bottom")
p1_ave

Res_1_ave <- Res_1
Res_1_ave$used <- "mean"
Res_1_max$used <- "max"
N_CAS_Site_1_ave <- N_CAS_Site_1
N_CAS_Site_1_ave$used <- "mean"
N_CAS_Site_1_max$used <- "max"
N_CAS_Site_1_2 <- rbind(N_CAS_Site_1_ave,N_CAS_Site_1_max)
Nclass_1_ave <- Nclass_1
Nclass_1_ave$used <- "mean"
Nclass_1_max$used <- "max"
Nclass_1_2 <- rbind(Nclass_1_ave,Nclass_1_max)

Res_1_2 <- rbind(Res_1_ave,Res_1_max)
Res_1_2$
p1_2 <- ggplot(Res_1_2,aes(x=HI_Chronic,y=MCR.HC05.Chronic.NOEC))+geom_point(aes(col=Group_AF1_Chronic))+geom_text(data=N_CAS_Site_1_2,aes(x=x,y=y,label=paste0("N.Site = ",N.Site,"\nN.CAS = ",N.CAS,"\nN.Sample = ",N.Sample)))+geom_text(data=Nclass_1_2,aes(x=x,y=y,label=paste0(Group,"\n",formatC(Perc,digits = 2,format="f"),"%")),vjust="inward")  +scale_x_log10()+geom_vline(xintercept = 1)+facet_grid(used~Exclusion.CAS,scale="free")+ annotate("rect", xmin = 1e-10, xmax = 1, ymin = recting[1,3], ymax = recting[1,4],fill="yellow",alpha=0.2)+geom_line(data=data.frame(x=seq(1,10,length=100),y=seq(1,10,length=100)),aes(x=x,y=y))+scale_y_continuous(limits=(c(1,10)),expand = c(0,0))+theme(legend.position = "bottom")
p1_2
ggsave("inst/manuscript_dropacute/Figure1-Chronic-2.png",width = 9,height=7,dpi=300)

# ggplot(Res_1,aes(x=HI_Chronic,y=MCR.HC05.Chronic.NOEC))+geom_point(aes(col=Group_AF1_Chronic))+geom_text(data=N_CAS_Site_1,aes(x=x,y=y,label=paste0("N.Site = ",N.Site,"\nN.CAS = ",N.CAS,"\nN.Sample = ",N.Sample)))+geom_text(data=Nclass_1,aes(x=x,y=y,label=paste0(Group,"\n",formatC(Perc,digits = 2,format="f"),"%")),vjust="inward")  +scale_x_log10()+geom_vline(xintercept = 1)+facet_grid(Exclusion.CAS~LOQ.type,scale="free")+ annotate("rect", xmin = 1e-10, xmax = 1, ymin = recting[1,3], ymax = recting[1,4],fill="yellow",alpha=0.2)+geom_line(data=data.frame(x=seq(1,10,length=100),y=seq(1,10,length=100)),aes(x=x,y=y))+scale_y_continuous(limits=(c(1,10)),expand = c(0,0))+theme(legend.position = "bottom")

if(interactive()){
  ggsave("inst/manuscript_dropacute/Figure1-Chronic.png",width = 9,height=6,dpi=300)
}
```


```{r}
N_CAS_Site_Chronic <- N_CAS_Site_1 %>% mutate(test="Chronic")
Nclass_Chronic <- Nclass_1 %>% mutate(test="Chronic")
Res_Chronic <- Res_1 %>% mutate(MCR=MCR.HC05.Chronic.NOEC,HI=HI_Chronic,Group_AF1=Group_AF1_Chronic)%>% mutate(test="Chronic")

```


```{r}
N_CAS_Site_1 <- rbind(N_CAS_Site_Acute,N_CAS_Site_Chronic)
 Nclass_1 <- rbind(Nclass_Acute,Nclass_Chronic)
 Res_1 <- rbind(Res_Acute,Res_Chronic)
 # Res_1$Group_AF1 <- NA
 # Res_1$Group_AF1[Res_1$test=="Acute"] <- Res_1$Group_AF1_Acute[Res_1$test=="Acute"]
 # Res_1$Group_AF1[Res_1$test=="Chronic"] <- Res_1$Group_AF1_Chronic[Res_1$test=="Chronic"]
 Res_1 <- Res_1 %>% rename(Group=Group_AF1)
 ggplot(Res_1,aes(x=HI,y=MCR))+geom_point(aes(col=Group))+geom_text(data=N_CAS_Site_1,aes(x=x,y=y*0.95,label=paste0("N.Site = ",N.Site,"\nN.CAS = ",N.CAS,"\nN.Sample = ",N.Sample)))+geom_text(data=Nclass_1,aes(x=x,y=y*0.8,label=paste0(Group,"\n",formatC(Perc,digits = 2,format="f"),"%")),vjust=1,hjust=0.8)  +scale_x_log10()+geom_vline(xintercept = 1)+facet_grid(test~Exclusion.CAS,scale="free")+ annotate("rect", xmin = 1e-10, xmax = 1, ymin = recting[1,3], ymax = recting[1,4],fill="yellow",alpha=0.2)+geom_line(data=data.frame(x=seq(1,10,length=100),y=seq(1,10,length=100)),aes(x=x,y=y))+scale_y_continuous(limits=(c(1,10)),expand = c(0,0))+theme(legend.position = "bottom",strip.text.x = element_text(size =12),strip.text.y = element_text(size = 12))
ggsave("inst/manuscript_cutoff_5measured/Figure1-final.png",width = 9,height=6,dpi=300)
if(interactive()){
  ggsave("inst/manuscript_cutoff_5measured/Figure1.png",width = 15,height=8,dpi=300)
}
```



## N measured > 10


```{r}
cutoff <- 10
Res <- Res%>%filter(Nmeasured>cutoff)
samples <- (Res%>%filter(Exclusion.CAS=="Current_Use"))
samples <- samples$monitoringSiteIdentifier
Res <- Res%>%filter(monitoringSiteIdentifier %in% samples)
dim(Res)
```


- save the table first before the plot

Table 1. CEFIC-MIAT Table 

- Include only AF 1 (Do we want to include other Afs?) 
- Chronic, same for Acute (for SM Materials) 
- LOQ.type = c("LOQ.T0", "LOQ.T1") 
- Exclusion.CAS = c("Excluded_None", "Excluded_Metals", "Current_Use") 
- Generate identical Table for Acute for SM. 

```{r}
N_CAS_Site_tmp <- Res %>% group_by(LOQ.type,Exclusion.CAS) %>% summarise(N.Site=length(unique(monitoringSiteIdentifier)),N.Sample=length(monitoringSiteIdentifier)) %>% mutate(Exclusion.CAS=factor(Exclusion.CAS,levels=c("Excluded_None","Refined_Metals_PAH","Excluded_Metals","Current_Use")))
table_chronic <- Res%>% group_by(LOQ.type,Exclusion.CAS,Group_AF1_Chronic) %>% summarise(N=length(monitoringSiteIdentifier))%>% ungroup %>% left_join(N_CAS_Site_tmp[,c("LOQ.type","Exclusion.CAS","N.Sample")])%>% mutate(Perc=N/N.Sample*100)
```


```{r}
if(interactive()){
  write.csv(table_chronic,file="inst/manuscript_cutoff_10measured/table_chronic_5measured.csv")
}

```


```{r}
table_chronic%>% knitr::kable(.,format = "html")%>%kableExtra::collapse_rows(.)
```


```{r}
table_acute <- Res%>% group_by(LOQ.type,Exclusion.CAS,Group_AF1_Acute) %>% summarise(N=length(monitoringSiteIdentifier))%>% ungroup %>% left_join(N_CAS_Site_tmp[,c("LOQ.type","Exclusion.CAS","N.Sample")])%>% mutate(Perc=N/N.Sample*100)
if(interactive()){
  write.csv(table_acute,file="inst/manuscript_cutoff_10measured/table_acute_5measured.csv")
}
```

```{r}
table_acute%>% knitr::kable(.,format = "html")%>%kableExtra::collapse_rows(.)
```


## Figure 1

```{r}
recting <- rbind(data.frame(xmin=-Inf,xmax=1,ymin=-Inf,ymax=Inf,col="green"),
                 data.frame(xmin=1,xmax=Inf,ymin=0,ymax=2,col="red"),
                  data.frame(xmin=1,xmax=Inf,ymin=2,ymax=Inf,col="yellow"))
```



```{r}
sum(Res$HI_Acute==0 & Res$Exclusion.CAS=="Excluded_None" & Res$LOQ.type=="LOQ.T0")
sum(Res$HI_Acute==0 & Res$Exclusion.CAS=="Excluded_None" & Res$LOQ.type=="LOQ.T1")

df <- data.frame(x=1e-6,y=9)

N_CAS_Site <- Res %>% group_by(LOQ.type,Exclusion.CAS) %>% summarise(N.Site=length(unique(monitoringSiteIdentifier)),N.Sample=length(monitoringSiteIdentifier)) %>% mutate(Exclusion.CAS=factor(Exclusion.CAS,levels=c("Excluded_None","Refined_Metals_PAH","Excluded_Metals","Current_Use")))
N.CAS <- sapply(c("Excluded_None","Refined_Metals_PAH","Excluded_Metals","Current_Use"),function(x)getNcas(x,chemclass))
N_CAS_Site$N.CAS <- rep(N.CAS[unique(N_CAS_Site$Exclusion.CAS)],2)
N_CAS_Site <- data.frame(df,N_CAS_Site)

Nclass <- Res %>% group_by(LOQ.type,Exclusion.CAS,Group_AF1_Acute) %>% summarise(N=length(monitoringSiteIdentifier))%>% left_join(N_CAS_Site[,c("LOQ.type","Exclusion.CAS","N.Sample")])%>% mutate(Perc=N/N.Sample*100)

Nclass1 <- Nclass %>% filter(Group_AF1_Acute=="IIIA" | Group_AF1_Acute =="IIIB")%>% group_by(LOQ.type,Exclusion.CAS) %>% summarise(Perc=sum(Perc)) %>% mutate(Group="III")

Nclass <- rbind(Nclass1,Nclass[,c("LOQ.type","Exclusion.CAS","Perc","Group_AF1_Acute")]%>%rename(Group=Group_AF1_Acute)%>%filter(Group=="I"|Group=="II"))

df1 <- data.frame(x=1e-6,y=7,Label="No concern",Group="II")
df1 <- rbind(df1,data.frame(x=20,y=5,Label="Single Substance Risk",Group="I"))
df1 <- rbind(df1,data.frame(x=5,y=10,Label="Multiple Chemicals Risk",Group="III"))
Nclass <- Nclass %>% left_join(df1)
```



```{r}
#ggplot(Res,aes(x=log10(HI_Acute),y=MCR.HC50.Acute.EC50))+geom_point()+geom_text(data=df,aes(x=x,y=y),label=paste0("N.Site = ",10,"\nN.CAS = ",5))+facet_grid(LOQ.type~Exclusion.CAS)
Res_1 <- Res %>% filter(LOQ.type=="LOQ.T0" & Exclusion.CAS != "Excluded_None") %>% droplevels(.)
N_CAS_Site_1 <- N_CAS_Site%>% filter(LOQ.type=="LOQ.T0" & Exclusion.CAS != "Excluded_None")%>% droplevels(.)
Nclass_1 <- Nclass%>% filter(LOQ.type=="LOQ.T0" & Exclusion.CAS != "Excluded_None")%>% droplevels(.)

ggplot(Res_1,aes(x=HI_Acute,y=MCR.HC50.Acute.EC50))+geom_point(aes(col=Group_AF1_Acute))+geom_text(data=N_CAS_Site_1,aes(x=x,y=y,label=paste0("N.Site = ",N.Site,"\nN.CAS = ",N.CAS,"\nN.Sample = ",N.Sample)))+geom_text(data=Nclass_1,aes(x=x,y=y,label=paste0(Group,"\n",formatC(Perc,digits = 2,format="f"),"%")),vjust="inward") +scale_x_log10()+geom_vline(xintercept = 1,col="blue")+geom_hline(yintercept = 2,col="blue")+facet_grid(LOQ.type~Exclusion.CAS,scale="free")+ annotate("rect", xmin = 1e-10, xmax = 1, ymin = recting[1,3], ymax = recting[1,4],fill="yellow",alpha=0.2)+geom_line(data=data.frame(x=seq(1,10,length=100),y=seq(1,10,length=100)),aes(x=x,y=y),col="blue")+theme(legend.position = "bottom")
# geom_rect(data=recting,aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax,fill=col))
# ggplot(data.frame(x=1:10,y=1:10),aes(x=x,y=y))+geom_point()+scale_x_log10()+ geom_line() 
if(interactive()){
  ggsave("inst/manuscript_cutoff_10measured/Figure1-Acute.png",width = 15,height=8,dpi=300)
}
```


- here we want to combine the acute and chronic results

```{r}
N_CAS_Site_Acute <- N_CAS_Site_1 %>% mutate(test="Acute")
Nclass_Acute <- Nclass_1 %>% mutate(test="Acute")
Res_Acute <- Res_1 %>% mutate(MCR=MCR.HC50.Acute.EC50,HI=HI_Acute,Group_AF1=Group_AF1_Acute)%>% mutate(test="Acute")

```


```{r}
N_CAS_Site$y <- 8


Nclass <- Res %>% group_by(LOQ.type,Exclusion.CAS,Group_AF1_Chronic) %>% summarise(N=length(monitoringSiteIdentifier))%>% left_join(N_CAS_Site[,c("LOQ.type","Exclusion.CAS","N.Sample")])%>% mutate(Perc=N/N.Sample*100)
Nclass1 <- Nclass %>% filter(Group_AF1_Chronic=="IIIA" | Group_AF1_Chronic =="IIIB")%>% group_by(LOQ.type,Exclusion.CAS) %>% summarise(Perc=sum(Perc)) %>% mutate(Group="III")

Nclass <- rbind(Nclass1,Nclass[,c("LOQ.type","Exclusion.CAS","Perc","Group_AF1_Chronic")]%>%rename(Group=Group_AF1_Chronic)%>%filter(Group=="I"|Group=="II"))

df1 <- data.frame(x=1e-6,y=4,Label="No concern",Group="II")
df1 <- rbind(df1,data.frame(x=50,y=5,Label="Single Substance Risk",Group="I"))
df1 <- rbind(df1,data.frame(x=5,y=9,Label="Multiple Chemicals Risk",Group="III"))
Nclass <- Nclass %>% left_join(df1)
Nclass_1 <- Nclass%>% filter(LOQ.type=="LOQ.T0" & Exclusion.CAS != "Excluded_None")%>% droplevels(.)

ggplot(Res_1,aes(x=HI_Chronic,y=MCR.HC05.Chronic.NOEC))+geom_point(aes(col=Group_AF1_Chronic))+geom_text(data=N_CAS_Site_1,aes(x=x,y=y,label=paste0("N.Site = ",N.Site,"\nN.CAS = ",N.CAS,"\nN.Sample = ",N.Sample)))+geom_text(data=Nclass_1,aes(x=x,y=y,label=paste0(Group,"\n",formatC(Perc,digits = 2,format="f"),"%")),vjust="inward")  +scale_x_log10()+geom_vline(xintercept = 1)+facet_grid(LOQ.type~Exclusion.CAS,scale="free")+ annotate("rect", xmin = 1e-10, xmax = 1, ymin = recting[1,3], ymax = recting[1,4],fill="yellow",alpha=0.2)+geom_line(data=data.frame(x=seq(1,10,length=100),y=seq(1,10,length=100)),aes(x=x,y=y))+scale_y_continuous(limits=(c(1,10)),expand = c(0,0))+theme(legend.position = "bottom")

# ggplot(Res_1,aes(x=HI_Chronic,y=MCR.HC05.Chronic.NOEC))+geom_point(aes(col=Group_AF1_Chronic))+geom_text(data=N_CAS_Site_1,aes(x=x,y=y,label=paste0("N.Site = ",N.Site,"\nN.CAS = ",N.CAS,"\nN.Sample = ",N.Sample)))+geom_text(data=Nclass_1,aes(x=x,y=y,label=paste0(Group,"\n",formatC(Perc,digits = 2,format="f"),"%")),vjust="inward")  +scale_x_log10()+geom_vline(xintercept = 1)+facet_grid(Exclusion.CAS~LOQ.type,scale="free")+ annotate("rect", xmin = 1e-10, xmax = 1, ymin = recting[1,3], ymax = recting[1,4],fill="yellow",alpha=0.2)+geom_line(data=data.frame(x=seq(1,10,length=100),y=seq(1,10,length=100)),aes(x=x,y=y))+scale_y_continuous(limits=(c(1,10)),expand = c(0,0))+theme(legend.position = "bottom")

if(interactive()){
  ggsave("inst/manuscript_cutoff_10measured/Figure1-Chronic.png",width = 15,height=8,dpi=300)
}
```


```{r}
N_CAS_Site_Chronic <- N_CAS_Site_1 %>% mutate(test="Chronic")
Nclass_Chronic <- Nclass_1 %>% mutate(test="Chronic")
Res_Chronic <- Res_1 %>% mutate(MCR=MCR.HC05.Chronic.NOEC,HI=HI_Chronic,Group_AF1=Group_AF1_Chronic)%>% mutate(test="Chronic")

```


```{r}
N_CAS_Site_1 <- rbind(N_CAS_Site_Acute,N_CAS_Site_Chronic)
 Nclass_1 <- rbind(Nclass_Acute,Nclass_Chronic)
 Res_1 <- rbind(Res_Acute,Res_Chronic)
 # Res_1$Group_AF1 <- NA
 # Res_1$Group_AF1[Res_1$test=="Acute"] <- Res_1$Group_AF1_Acute[Res_1$test=="Acute"]
 # Res_1$Group_AF1[Res_1$test=="Chronic"] <- Res_1$Group_AF1_Chronic[Res_1$test=="Chronic"]
 Res_1 <- Res_1 %>% rename(Group=Group_AF1)
 ggplot(Res_1,aes(x=HI,y=MCR))+geom_point(aes(col=Group))+geom_text(data=N_CAS_Site_1,aes(x=x,y=y*0.95,label=paste0("N.Site = ",N.Site,"\nN.CAS = ",N.CAS,"\nN.Sample = ",N.Sample)))+geom_text(data=Nclass_1,aes(x=x,y=y*0.8,label=paste0(Group,"\n",formatC(Perc,digits = 2,format="f"),"%")),vjust=1,hjust=0.8)  +scale_x_log10()+geom_vline(xintercept = 1)+facet_grid(test~Exclusion.CAS,scale="free")+ annotate("rect", xmin = 1e-10, xmax = 1, ymin = recting[1,3], ymax = recting[1,4],fill="yellow",alpha=0.2)+geom_line(data=data.frame(x=seq(1,10,length=100),y=seq(1,10,length=100)),aes(x=x,y=y))+scale_y_continuous(limits=(c(1,10)),expand = c(0,0))+theme(legend.position = "bottom",strip.text.x = element_text(size =12),strip.text.y = element_text(size = 12))
ggsave("inst/manuscript_cutoff_10measured/Figure1-final.png",width = 9,height=6,dpi=300)
if(interactive()){
  ggsave("inst/manuscript_cutoff_10measured/Figure1.png",width = 15,height=8,dpi=300)
}
```

