---
title: "msPAF"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{msPAF}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval=T,
  fig.width = 12,
  fig.height = 10
)
```


- Spatial bias and substance selection bias?


## Heatmap on the map

- [ ] add MCR based classification
- [x] Do we need N measured?
- [ ] add missing countries

```{r}
library(ggplot2)
library(dplyr)
require(maps)
require(viridis)
theme_set(
  theme_void()
  )
library(RColorBrewer)
```

"BA" "BE" "CH" "CY" "CZ" "DE" "ES" "FI" "FR" "HR" "IE" "IT" NA   "LT" "LU" "LV" "NL" "PL" "RO" "RS" "SE"
"SK" "UK"

```{r}
# Some EU Contries
some.eu.countries <- c(
  "Portugal", "Spain", "France", "Switzerland", "Germany",
  "Austria", "Belgium", "UK", "Netherlands",
  "Denmark", "Poland", "Italy", "Cyprus",
  "Croatia", "Slovenia", "Hungary", "Slovakia",
  "Czech republic","Denmark","Finland","Sweden","Bosnia and Herzegovina","Ireland","Lithuania","Luxembourg","Latvia","Poland","Romania","Serbia","Slovakia","Czechia"
)
# Retrievethe map data
some.eu.maps <- map_data("world", region = some.eu.countries)

# Compute the centroid as the mean longitude and lattitude
# Used as label coordinate for country's names
region.lab.data <- some.eu.maps %>%
  group_by(region) %>%
  summarise(long = mean(long), lat = mean(lat))



cols <- brewer.pal(n = 9, name = 'Paired')
stations1$popup <- with(stations1, paste("<b>", monitoringSiteIdentifier, "</b>"))
#stations1$col <- plyr::mapvalues(stations1$countryCode,from=unique(stations1$countryCode),to=cols)
stations1$lon <- as.numeric(stations1$lon)
stations1$lat <- as.numeric(stations1$lat)
```


```{r}
ggplot(some.eu.maps, aes(x = long, y = lat)) +
  geom_polygon(aes( group = group),fill=NA,col="black",guide=F)+
  scale_fill_viridis_d(option="plasma")+
  theme_void()+
  geom_point(data=stations1%>%filter(LOQ.type=="LOQ.T0" & Exclusion.CAS=="Excluded_None"),aes(x = lon, y = lat,col=log(mean_HI_Acute)),size=0.1)+geom_text(aes(label = region), data = region.lab.data,  size = 3, hjust = 0.5)+scale_color_viridis_c(direction=-1,option = "inferno")+guides(fill=FALSE,alpha=FALSE)
```


```{r}
if(interactive()){
  ggsave("inst/manuscript/map_T0_None.png",width = 8,height=8,dpi=300)
}
```


```{r}
ggplot(data=stations1%>%filter(Exclusion.CAS != "Excluded_None"& Exclusion.CAS != "Refined_Metals_PAH"),aes(x = lon, y = lat))+geom_point(aes(col=(mean_HI_Chronic)),size=0.1)+
  geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+
scale_color_viridis_b(trans="log10",direction=-1,option = "D")+guides(fill=FALSE,alpha=FALSE)+facet_grid(LOQ.type~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,40))+ylim(c(30,70))


if(interactive()){
  ggsave("inst/manuscript_v3/map_mean_HI_Chronic.png",width = 10,height=8,dpi=300)
}


ggplot(data=stations1%>%filter(Exclusion.CAS != "Excluded_None"& Exclusion.CAS != "Refined_Metals_PAH"),aes(x = lon, y = lat))+geom_point(aes(col=(mean_HI_Acute)))+
  geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+
scale_color_viridis_c(trans="log10",direction=-1,option = "D")+guides(fill=FALSE,alpha=FALSE)+facet_grid(LOQ.type~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,40))+ylim(c(30,70))
#  +
#   theme(  legend.title.align = 0.5,
#           legend.text.align = 0.5,
#           legend.text = element_text(angle=45),
#           legend.justification = c(0.5, 0.5),
#           legend.position = "bottom"
#           )


if(interactive()){
  ggsave("inst/manuscript_v3/map_mean_HI_Acute.png",width = 10,height=8,dpi=300)
}


stdata <- stations1%>%filter(Exclusion.CAS != "Excluded_None" & Exclusion.CAS != "Refined_Metals_PAH" & LOQ.type=="LOQ.T0") %>% pivot_longer(cols=c(mean_N_measured,mean_N_detected),names_to="Ntype",values_to="N")
stdata$Ntype <- factor(stdata$Ntype,levels=c("mean_N_measured","mean_N_detected"))
stdata$Exclusion.CAS <- factor(stdata$Exclusion.CAS,levels=c("Excluded_Metals","Banned_Listed","Current_Use"))
ggplot(stdata,aes(x = lon, y = lat))+geom_point(aes(col=N))+
  geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+
scale_color_viridis_c(trans="log10",direction=-1,option = "D")+guides(fill=FALSE,alpha=FALSE)+facet_grid(Ntype~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,40))+ylim(c(30,70))


if(interactive()){
  ggsave("inst/manuscript_v3/map_mean_N_measure.png",width=10,height=8,dpi=300)
}


ggplot(data=stations1%>%filter(Exclusion.CAS != "Excluded_None"& Exclusion.CAS != "Refined_Metals_PAH"),aes(x = lon, y = lat))+geom_point(aes(col=(mean_MCR_Acute)))+  geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+scale_color_viridis_c(direction=-1,option = "D")+guides(fill=FALSE,alpha=FALSE)+facet_grid(LOQ.type~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,40))+ylim(c(30,70))+xlim(c(-11,40))+ylim(c(30,70))


if(interactive()){
  ggsave("inst/manuscript_v3/map_mean_MCR_Acute.png",width=10,height=8,dpi=300)
}


ggplot(data=stations1%>%filter(Exclusion.CAS != "Excluded_None"& Exclusion.CAS != "Refined_Metals_PAH"),aes(x = lon, y = lat))+geom_point(aes(col=(mean_MCR_Chronic)))+
  geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+
scale_color_viridis_c(direction=-1,option = "D")+guides(fill=FALSE,alpha=FALSE)+facet_grid(LOQ.type~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,40))+ylim(c(30,70))


if(interactive()){
  ggsave("inst/manuscript_v3/map_mean_MCR_Chronic.png",width=10,height=8,dpi=300)
}




ggplot(data=stations1%>%filter(Exclusion.CAS != "Excluded_None"& Exclusion.CAS != "Banned_Listed"),aes(x = lon, y = lat))+geom_point(aes(col=(Group_AF1_Acute)))+  geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+scale_color_viridis_d(direction=-1,option = "D")+guides(fill=FALSE,alpha=FALSE)+facet_grid(LOQ.type~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,40))+ylim(c(30,70))+xlim(c(-11,40))+ylim(c(30,70))


if(interactive()){
  ggsave("inst/manuscript_v3/map_Group_AF1__Acute.png",width=10,height=8,dpi=300)
}


ggplot(data=stations1%>%filter(Exclusion.CAS != "Excluded_None"),aes(x = lon, y = lat))+geom_point(aes(col=(Group_AF1_Chronic)))+
  geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+
scale_color_viridis_d(direction=-1,option = "D")+guides(fill=FALSE,alpha=FALSE)+facet_grid(LOQ.type~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,40))+ylim(c(30,70))


if(interactive()){
  ggsave("inst/manuscript_v3/map_Group_AF1_Chronic.png",width=10,height=8,dpi=300)
}
```




- use excluded_metals & PAH 

```{r}
cols <- brewer.pal(n = 9, name = 'Paired')
stations2$popup <- with(stations2, paste("<b>", monitoringSiteIdentifier, "</b>"))
#stations2$col <- plyr::mapvalues(stations2$countryCode,from=unique(stations2$countryCode),to=cols)
stations2$lon <- as.numeric(stations2$lon)
stations2$lat <- as.numeric(stations2$lat)
```


```{r}
ggplot(data=stations2,aes(x = lon, y = lat))+geom_point(aes(col=(mean_HI_Chronic)))+
  geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+
scale_color_viridis_c(trans="log10",direction=-1,option = "B")+guides(fill=FALSE,alpha=FALSE)+facet_grid(LOQ.type~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,40))+ylim(c(30,70))


if(interactive()){
  ggsave("inst/manuscript_v2/map_mean_HI_Chronic.png",width=10,height=8,dpi=300)
}


ggplot(data=stations2,aes(x = lon, y = lat))+geom_point(aes(col=(mean_HI_Acute)))+
  geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+
scale_color_viridis_c(trans="log10",direction=-1,option = "D")+guides(fill=FALSE,alpha=FALSE)+facet_grid(LOQ.type~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,40))+ylim(c(30,70))+xlim(c(-11,40))+ylim(c(30,70))


if(interactive()){
  ggsave("inst/manuscript_v2/map_mean_HI_Acute.png",width=10,height=8,dpi=300)
}


ggplot(data=stations2,aes(x = lon, y = lat))+geom_point(aes(col=(mean_N_measured)))+
  geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+
scale_color_viridis_c(trans="log10",direction=-1,option = "D")+guides(fill=FALSE,alpha=FALSE)+facet_grid(LOQ.type~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,40))+ylim(c(30,70))


if(interactive()){
  ggsave("inst/manuscript_v2/map_mean_N_measure.png",width=10,height=8,dpi=300)
}

ggplot(data=stations2,aes(x = lon, y = lat))+geom_point(aes(col=(mean_MCR_Acute)))+
  geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+
scale_color_viridis_c(direction=-1,option = "D")+guides(fill=FALSE,alpha=FALSE)+facet_grid(LOQ.type~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,40))+ylim(c(30,70))


if(interactive()){
  ggsave("inst/manuscript_v2/map_mean_MCR_Acute.png",width=10,height=8,dpi=300)
}


ggplot(data=stations2,aes(x = lon, y = lat))+geom_point(aes(col=(mean_MCR_Chronic)))+
  geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+
scale_color_viridis_c(trans="log10",direction=-1,option = "D")+guides(fill=FALSE,alpha=FALSE)+facet_grid(LOQ.type~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,40))+ylim(c(30,70))


if(interactive()){
  ggsave("inst/manuscript_v2/map_mean_MCR_Chronic.png",width=10,height=8,dpi=300)
}




ggplot(data=stations2,aes(x = lon, y = lat))+geom_point(aes(col=(Group_AF1_Acute)))+  geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+scale_color_viridis_d(direction=-1,option = "D")+guides(fill=FALSE,alpha=FALSE)+facet_grid(LOQ.type~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,40))+ylim(c(30,70))+xlim(c(-11,40))+ylim(c(30,70))


if(interactive()){
  ggsave("inst/manuscript_v2/map_Group_AF1_Acute.png",width=10,height=8,dpi=300)
}


ggplot(data=stations2,aes(x = lon, y = lat))+geom_point(aes(col=(Group_AF1_Chronic)))+
  geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+
scale_color_viridis_d(direction=-1,option = "D")+guides(fill=FALSE,alpha=FALSE)+facet_grid(LOQ.type~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,40))+ylim(c(30,70))


if(interactive()){
  ggsave("inst/manuscript_v2/map_Group_AF1_Chronic.png",width=10,height=8,dpi=300)
}
```




```{r}
library(rworldmap)
newmap <- getMap(resolution = "low")
library(ggmap)
# europe.limits <- geocode(c("CapeFligely,RudolfIsland,Franz Josef Land,Russia",
#    "Gavdos,Greece",
#    "Faja Grande,Azores","SevernyIsland,Novaya Zemlya,Russia"))

plot(newmap,
   xlim = c(-20, 59),
   ylim = c(35, 71),
   asp = 1
 )
 
 
```



```{r eval=F,include=F}
library(leaflet)
library(dplyr)

cols <- c("darkred", "orange", "darkblue", "lightgreen", "blue","pink","green","darkgreen","purple")
stations$popup <- with(stations, paste("<b>", monitoringSiteIdentifier, "</b>"))
stations$col <- plyr::mapvalues(stations$countryCode,from=unique(stations$countryCode),to=cols)
colors()[match(rgb(t(col2rgb(brewer.pal(n = 9, name = 'Paired'))), 
    maxColorValue = 255), c(rgb(t(col2rgb(colors())), maxColorValue = 255)))]

stations$lon <- as.numeric(stations$lon)
stations$lat <- as.numeric(stations$lat)
markers <- awesomeIcons(
    icon='map-marker',
    iconColor = 'black',
    markerColor = stations$col,
    library='fa')

m <- leaflet(data = stations, width = "100%" ) %>%
    addTiles() %>%  # Add default OpenStreetMap map tiles
    addAwesomeMarkers(
        lng = ~lon, 
        lat = ~lat, 
        popup = ~popup,
        icon = markers
    ) %>%
    addLegend(
        position='topright',
        colors= cols,
        labels= unique(stations$countryCode),
        opacity = 0.75,
        title="Legend"
        )

m  # Show map
```


## Sunburst Chart

- Chemical space: class and regulatory status


```{r}
chemclass$class1 <- chemclass$class
chemclass$class1[chemclass$Chem.Group=="PAH"] <- "PAH"
tmp <- chemclass %>% group_by(class1,Chem.Group) %>% summarise(num=length(CAS))
parent <- tmp$class1
labels <- paste0(tmp$Chem.Group," (",tmp$num,")")
values <- tmp$num
ids <- paste0(parent,"-",labels)
tmp <- chemclass %>% group_by(class1) %>% summarise(num=length(CAS))
parent <- c("",rep("All",nrow(tmp)),parent)
labels <- c("All (334)",paste0(tmp$class1," (",tmp$num,")"),labels)
values <- c(334,tmp$num,values)
ids <- c("All",tmp$class1,ids)

d <- data.frame(parent,labels,values,ids)
library(plotly)


write.csv(d,file="./inst/manuscript_v3/chemclass_nsub.csv")


fig <- plot_ly(d,
    ids=~ids, 
  labels = ~labels,
  parents = ~parent,
  values =~values,
  type = 'sunburst',
  branchvalues = 'total',
  marker = list(colors = list("#FFFFFF","#FF8000","#009900","#800080"))
)
fig
```


- Chemical space: class and N measured, N detected! as labels
- downloaded to the folder inst/manuscript/chemclass_detected_measured.png

```{r}
 cheminfo <- Data.AggBySiteID.2 %>%left_join(chemclass)%>%
    dplyr::group_by(class,Site.Year,Chem.Group) %>% dplyr::summarise(Detected=any(AboveLOQ),Measured=length(Chem.Group)>0) %>%
    ungroup %>% group_by(class,Chem.Group) %>% dplyr::summarise(Ndetected=sum(Detected),Nmeasured=sum(Measured))##%>%
##    ungroup %>% group_by(class) %>% ## mutate(Ndetected.class=sum(Ndetected),Nmeasured.class=sum(Nmeasured))
tmp <- Data.AggBySiteID.2 %>%left_join(chemclass)%>%
    dplyr::group_by(class,Site.Year) %>% dplyr::summarise(Detected=any(AboveLOQ),Measured=length(Chem.Group)>0) %>%
    ungroup %>% group_by(class) %>% dplyr::summarise(Ndetected=sum(Detected),Nmeasured=sum(Measured))

parent <- cheminfo$class
labels <- paste0(cheminfo$Chem.Group,"\n",cheminfo$Ndetected,"\n",cheminfo$Nmeasured)
values <- cheminfo$Nmeasured
ids <- paste0(parent,"-",labels)

parent <- c("",rep("All",nrow(tmp)),parent)
labels <- c("All (12356)",paste0(tmp$class,"\n",tmp$Ndetected,"\n",tmp$Nmeasured),labels)
values <- c(12356,tmp$Nmeasured,values)
ids <- c("All",tmp$class,ids)

d <- data.frame(parent,labels,values,ids)
library(plotly)





fig <- plot_ly(d,
    ids=~ids, 
  labels = ~labels,
  parents = ~parent,
  values =~values,
  type = 'sunburst'
)
fig
```




- https://plotly.com/r/sunburst-charts/
- https://stackoverflow.com/questions/12926779/how-to-make-a-sunburst-plot-in-r-or-python
- https://medium.com/optima-blog/create-basic-sunburst-graphs-with-ggplot2-7d7484d92c61


## Driver Plots with LOQ.T1 option

```{r}
driverdata <- getDriverData(Data.AggBySiteID.2,chemclass,LOQ.type = c("LOQ.T1"), Exclusion.CAS = c("Refined_Metals_PAH", "Excluded_Metals_PAH","Current_Use"), Data.SSD.1,threshold = 1)
```

```{r}
site.year <- driverdata%>%filter(Exclusion.CAS=="Excluded_Metals_PAH",test=="Chronic") %>% group_by(LOQ.type)%>% nest()%>%mutate(sy=map(data,function(df)unique(df$Site.Year)))
## extract driver data with the same site.year.

currentdat <- getDriverData(Data.AggBySiteID.2,chemclass,LOQ.type = c("LOQ.T1"),
Exclusion.CAS = c("Current_Use"),Data.SSD.1, threshold=0.1)
currentdat <- currentdat %>% filter(test=="Chronic")
# tmp1 <- currentdat %>% filter(LOQ.type=="LOQ.T0") %>% filter(Site.Year %in% site.year$sy[[1]])
tmp2 <- currentdat %>% filter(LOQ.type=="LOQ.T1") %>% filter(Site.Year %in% site.year$sy[[2]])
# currentdat1 <- rbind(tmp1,tmp2)%>%group_by(LOQ.type) %>% nest()%>% mutate(data=purrr::map(data,function(df){
#   df1<- df%>%group_by(Site.Year,monitoringSiteIdentifier,phenomenonTimeReferenceYear,HI) %>% nest()
#   df <- df1[order(df1$HI,decreasing = T),]%>% add_column(x=1:nrow(df1))%>%unnest(cols = c(data))%>% ungroup
#   return(df)}))%>%unnest(cols = c(data))%>%mutate(Component=factor(Component,levels=c("Driver 1","Driver 2","Driver 3","All Other" )))

currentdat1 <- tmp2 %>%group_by(LOQ.type) %>% nest()%>% mutate(data=purrr::map(data,function(df){
  df1<- df%>%group_by(Site.Year,monitoringSiteIdentifier,phenomenonTimeReferenceYear,HI) %>% nest()
  df <- df1[order(df1$HI,decreasing = T),]%>% add_column(x=1:nrow(df1))%>%unnest(cols = c(data))%>% ungroup
  return(df)}))%>%unnest(cols = c(data))%>%mutate(Component=factor(Component,levels=c("Driver 1","Driver 2","Driver 3","All Other" )))
```



```{r}

nsample1 <- driverdata1 %>% group_by(LOQ.type,Exclusion.CAS,test)%>% nest()%>%mutate(sy=map(data,function(df) length(unique(df$Site.Year))),hmax=map(data,function(df) max(df$HI)))%>% select(-data) %>% unnest(cols=c(sy,hmax)) %>% mutate(Exclusion.CAS=factor(Exclusion.CAS,levels=c("Refined_Metals_PAH","Excluded_Metals_PAH","Current_Use")))
```


```{r}
chemclass <- chemclass %>% mutate(CAS=as.character(CAS))
table13 <- driverdata1 %>% left_join(Res%>%filter(LOQ.type=="LOQ.T1" & Exclusion.CAS!="Excluded_None"))%>% group_by(LOQ.type, Exclusion.CAS,Group_AF1_Chronic) %>% mutate(N=length(unique(Site.Year))) %>% filter(Component!="All Other")%>% group_by(LOQ.type, Exclusion.CAS,Group_AF1_Chronic,N,CAS) %>% summarise(HQmax=max(HQ,na.rm=T),N1=sum(HQ>1,na.rm=T),N2=sum(HQ>0.5,na.rm = T),N3=sum(HQ>0.1)) %>% filter((Group_AF1_Chronic=="I" & N1>0) | (Group_AF1_Chronic=="IIIA" & N2>0) | (Group_AF1_Chronic=="IIIB" & N3>0)) %>% left_join(chemclass) %>% dplyr::select(c('LOQ.type', 'Exclusion.CAS', 'Group_AF1_Chronic', 'N',"Substance","HQmax","N1","N2","N3"))
```


```{r}
write.csv(table13,file="inst/manuscript_v3/table13_LOQ.T1.csv")
```
