---
title: "Manuscript Supplemental Information"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(beemixtox)
library(tidyverse)
```

```{r}
summaryN <- function(x){
  nsum <- quantile(x,c(0,0.25,0.5,0.75,1),na.rm = T)
  nsum <- c(nsum[1:3],mean(x,na.rm = T),nsum[4:5])
  names(nsum)[4] <- "mean"
  nsum <- as.data.frame(t(nsum))  
  return(nsum)
}
```


## Data Curation

Note that the complete raw data is not directly available via the supplemental package. In this section only the code to generate the relevant tables and figures are provided. To check the data curation process, please go to folder /data-raw/ and check DATASET.R. 

```{r}
length(unique(stations$countryCode))
length(unique(stations$waterBodyIdentifier))
```

```{r}
Data.AggBySiteID.3a <-  preprocessWaterbase(Data.AggBySiteID.2,chemclass,LOQ.type = "LOQ.T0",
                                              Data.SSD.1 = Data.SSD.1,Exclusion.CAS="Refined_Metals_PAH")
write_csv(Data.AggBySiteID.3a,"WB_refined_metals_PAH_T0.csv")
```




### Supplemental Info: Fig 2

```{r eval=F}
a <- Data.AggBySiteID.2%>%group_by(phenomenonTimeReferenceYear) %>% summarise(nsample=n()) %>% arrange(phenomenonTimeReferenceYear)%>%mutate(Data="After Data Curation")
b <- Data.AggBySiteID %>% group_by(phenomenonTimeReferenceYear) %>% summarise(nsample=n()) %>% arrange(phenomenonTimeReferenceYear)%>%mutate(Data="After Data Selection")
yeardata <- rbind(a,b)%>%mutate(Data=factor(Data,levels=c("After Data Selection","After Data Curation")))
yeardata <- yeardata%>%pivot_wider(names_from = phenomenonTimeReferenceYear,values_from=nsample) %>% as.data.frame (.)%>%replace(is.na(.), 0) %>% pivot_longer(cols = -1,names_to="phenomenonTimeReferenceYear",values_to="nsample")
ggplot(yeardata,aes(x=phenomenonTimeReferenceYear,y=nsample,col=Data,fill=Data))+geom_bar(stat="identity",position ="dodge")+labs(x="Year",y="Number of Samples")+theme(legend.position = "bottom",axis.text.x = element_text(angle=-90))+scale_x_discrete(breaks=as.character(seq(1931,2020,by=5)))
if(interactive()){
  ggsave("~/Projects/beemixtox/inst/manuscript_2022/supp_fig2.png",width=5,height=3)
  ggsave("~/Projects/beemixtox/inst/manuscript_2022/supp_fig2.pdf",width=5,height=3)
} 
```

### Supplemental Info: Fig 1



```{r eval=F}
tmp <-  Data.AggBySiteID.2%>%left_join(stations)
a <- tmp%>%group_by(countryCode) %>% summarise(nsample=n()) %>% arrange(countryCode)%>%mutate(Data="After Data Curation")
tmp <- Data.AggBySiteID %>%left_join(stations)
b <-   tmp%>%group_by(countryCode) %>% summarise(nsample=n()) %>% arrange(countryCode)%>%mutate(Data="After Data Selection")
countrydata <- rbind(a,b)%>%mutate(Data=factor(Data,levels=c("After Data Selection","After Data Curation")))
countrydata <- countrydata%>%pivot_wider(names_from = countryCode,values_from=nsample) %>% as.data.frame (.)%>%replace(is.na(.), 0) %>% pivot_longer(cols = -1,names_to="countryCode",values_to="nsample")
ggplot(countrydata,aes(x=countryCode,y=nsample,col=Data,fill=Data))+geom_bar(stat="identity",position ="dodge")+labs(x="Country",y="Number of Samples")+theme(legend.position = "bottom",axis.text.x = element_text(angle=-90))
if(interactive()) {
  ggsave("~/Projects/beemixtox/inst/manuscript_2022/supp_fig1.png",width=5,height=3)
  ggsave("~/Projects/beemixtox/inst/manuscript_2022/supp_fig1.pdf",width=5,height=3)
}
```


```{r}

ggplot(countrydata%>%filter(countryCode!="NA"),aes(x=countryCode,y=nsample,col=Data,fill=Data))+geom_bar(stat="identity",position ="dodge")+labs(x="Country",y="Number of Samples")+theme(legend.position = "bottom",axis.text.x = element_text(angle=-90))
if(interactive()) {
  ggsave("~/Projects/beemixtox/inst/manuscript_2022/supp_fig1_rmNA.png",width=5,height=3)
  ggsave("~/Projects/beemixtox/inst/manuscript_2022/supp_fig1_rmNA.pdf",width=5,height=3)
}

```



```{r eval=F}
Res1 <-  getResData(Data.AggBySiteID.2,chemclass,LOQ.type = c("LOQ.T0"),
            Exclusion.CAS = c("Excluded_None"),Data.SSD.1)
Data.AggBySiteID.2 %>%left_join(chemclass) %>% group_by(Chem.Group) %>% summarise(AboveLOQ=sum(AboveLOQ)/n()*100, BelowLOQ = 100-AboveLOQ)

Data.AggBySiteID.2 %>%left_join(chemclass) %>% group_by(class) %>% summarise(AboveLOQ=sum(AboveLOQ)/n()*100, BelowLOQ = 100-AboveLOQ)
Data.AggBySiteID.2 %>%summarise(AboveLOQ=sum(AboveLOQ)/n()*100, BelowLOQ = 100-AboveLOQ)
```

## Table LOQ Summary:

```{r}
Res1 <-  getResData(Data.AggBySiteID.2,chemclass,LOQ.type = c("LOQ.T0"),
            Exclusion.CAS = c("Excluded_None"),Data.SSD.1)
Data.AggBySiteID.2 %>%left_join(chemclass) %>% group_by(Chem.Group) %>% summarise(AboveLOQ=sum(AboveLOQ)/n()*100, BelowLOQ = 100-AboveLOQ)

Data.AggBySiteID.2 %>%left_join(chemclass) %>% group_by(class) %>% summarise(AboveLOQ=sum(AboveLOQ)/n()*100, BelowLOQ = 100-AboveLOQ)
Data.AggBySiteID.2 %>%summarise(AboveLOQ=sum(AboveLOQ)/n()*100, BelowLOQ = 100-AboveLOQ)
```


```{r}
Data.AggBySiteID.2 %>%left_join(chemclass) %>% group_by(Chem.Group) %>% nest() %>% mutate(nsum=map(data,~summaryN(.x$procedureLOQValue)))%>% select(-data)%>% unnest(cols=c(nsum)) %>%  dplyr::mutate_at(c("0%","25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.) %>% kableExtra::kable_classic() 
```


## Table 6: Cas Data HC50 Acute Summary

```{r}
casdata %>% summarise(n=n())
summaryN(casdata$HC05.Chronic) %>% dplyr::mutate_at(c("0%","25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.) %>% kableExtra::kable_classic()

summaryN(casdata$HC50.Acute) %>% dplyr::mutate_at(c("0%","25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.) %>% kableExtra::kable_classic()

## casdata %>% summarise(nsum=map(HC50.Acute,summaryN))
```


```{r}
casdata %>% group_by(Chem.Group)%>% nest() %>% mutate(n1=map(data,~nrow(.x)))%>%mutate(nsum=map(data,~summaryN(.x$HC50.Acute)))%>% select(-data)%>% unnest(cols=c(n1,nsum)) %>%  dplyr::mutate_at(c("0%","25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.) %>% kableExtra::kable_classic()
```


```{r}
casdata %>% group_by(Chem.Group,Type)%>% nest() %>% mutate(n1=map(data,~nrow(.x)))%>%mutate(nsum=map(data,~summaryN(.x$HC50.Acute)))%>% select(-data)%>% unnest(cols=c(n1,nsum)) %>%  dplyr::mutate_at(c("0%","25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.) %>% kableExtra::kable_classic()
```


```{r}
casdata$Type <- factor(casdata$Type,levels=c("I","H","F"))
casdata %>% group_by(Type)%>% nest() %>% mutate(n1=map(data,~nrow(.x)))%>%mutate(nsum=map(data,~summaryN(.x$HC50.Acute)))%>% select(-data)%>% unnest(cols=c(n1,nsum)) %>% #dplyr::mutate_if(is.numeric, ~(as.character(signif(., 3))))%>% 
  dplyr::mutate_at(c("0%",   "25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.) %>% kableExtra::kable_classic()
```

```{r include=FALSE}
which(casdata$Chem.Group=="Pest" & !(casdata$Type %in% c("H","I","F")))
```


```{r}
casdata%>%filter(class=="Banned_Listed") %>% group_by(1)%>% nest() %>% mutate(n1=map(data,~nrow(.x)))%>%mutate(nsum=map(data,~summaryN(.x$HC50.Acute)))%>% select(-data)%>% unnest(cols=c(n1,nsum)) %>% #dplyr::mutate_if(is.numeric, ~(as.character(signif(., 3))))%>% 
  dplyr::mutate_at(c("0%",   "25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.,caption="Legacy") %>% kableExtra::kable_classic()
```

```{r}
casdata%>%filter(class=="Banned_Listed") %>% group_by(Chem.Group)%>% nest() %>% mutate(n1=map(data,~nrow(.x)))%>%mutate(nsum=map(data,~summaryN(.x$HC50.Acute)))%>% select(-data)%>% unnest(cols=c(n1,nsum)) %>%arrange(Chem.Group)%>%
  dplyr::mutate_at(c("0%",   "25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.,caption="HC50, Legacy") %>% kableExtra::kable_classic_2()
```

```{r}
casdata%>%filter(class=="Banned_Listed") %>% group_by(Chem.Group,Type)%>% nest() %>% mutate(n1=map(data,~nrow(.x)))%>%mutate(nsum=map(data,~summaryN(.x$HC50.Acute)))%>% select(-data)%>% unnest(cols=c(n1,nsum))  %>%arrange(Chem.Group,Type)%>%
  dplyr::mutate_at(c("0%",   "25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.,caption="HC50, Legacy") %>% kableExtra::kable_classic_2()
```



```{r}
casdata%>%filter(class=="Current_Use") %>% group_by(Chem.Group)%>% nest() %>% mutate(n1=map(data,~nrow(.x)))%>%mutate(nsum=map(data,~summaryN(.x$HC50.Acute)))%>% select(-data)%>% unnest(cols=c(n1,nsum)) %>% #dplyr::mutate_if(is.numeric, ~(as.character(signif(., 3))))%>% 
  dplyr::mutate_at(c("0%",   "25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.,caption="Current Use") %>% kableExtra::kable_classic_2()
```

```{r}
casdata%>%filter(class=="Current_Use") %>% group_by(1)%>% nest() %>% mutate(n1=map(data,~nrow(.x)))%>%mutate(nsum=map(data,~summaryN(.x$HC50.Acute)))%>% select(-data)%>% unnest(cols=c(n1,nsum)) %>% #dplyr::mutate_if(is.numeric, ~(as.character(signif(., 3))))%>% 
  dplyr::mutate_at(c("0%",   "25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.,caption="Current Use") %>% kableExtra::kable_classic_2()

```


```{r}
casdata%>%filter(class=="Current_Use") %>% group_by(Chem.Group)%>% nest() %>% mutate(n1=map(data,~nrow(.x)))%>%mutate(nsum=map(data,~summaryN(.x$HC50.Acute)))%>% select(-data)%>% unnest(cols=c(n1,nsum)) %>% #dplyr::mutate_if(is.numeric, ~(as.character(signif(., 3))))%>% 
  dplyr::mutate_at(c("0%",   "25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.,caption="Current Use") %>% kableExtra::kable_classic_2()
```

```{r}
casdata%>%filter(class=="Current_Use") %>% group_by(Chem.Group,Type)%>% nest() %>% mutate(n1=map(data,~nrow(.x)))%>%mutate(nsum=map(data,~summaryN(.x$HC50.Acute)))%>% select(-data)%>% unnest(cols=c(n1,nsum)) %>% #dplyr::mutate_if(is.numeric, ~(as.character(signif(., 3))))%>% 
  dplyr::mutate_at(c("0%",   "25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.,caption="Current Use") %>% kableExtra::kable_classic_2()
``` 





## Table 7: Cas Data HC05 Chronic

```{r}
casdata$Type <- factor(casdata$Type,levels=c("I","H","F",""))
casdata$Chem.Group <- factor(casdata$Chem.Group,levels=c("Industrial", "Metal", "PAH", "Pest", "Pharma"))
```


```{r}

casdata %>% group_by(1)%>% nest() %>% mutate(n1=map(data,~nrow(.x)))%>%mutate(nsum=map(data,~summaryN(.x$HC05.Chronic)))%>% select(-data)%>% unnest(cols=c(n1,nsum)) %>% #arrange(Chem.Group)%>%
  dplyr::mutate_at(c("0%",   "25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.,caption="HC05, All") %>% kableExtra::kable_classic_2()
```


```{r}

casdata %>% group_by(Chem.Group)%>% nest() %>% mutate(n1=map(data,~nrow(.x)))%>%mutate(nsum=map(data,~summaryN(.x$HC05.Chronic)))%>% select(-data)%>% unnest(cols=c(n1,nsum)) %>% arrange(Chem.Group)%>%
  dplyr::mutate_at(c("0%",   "25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.,caption="HC05, All") %>% kableExtra::kable_classic_2()
```


```{r}
casdata %>% group_by(Chem.Group,Type)%>% nest() %>% mutate(n1=map(data,~nrow(.x)))%>%mutate(nsum=map(data,~summaryN(.x$HC05.Chronic)))%>% select(-data)%>% unnest(cols=c(n1,nsum)) %>%arrange(Chem.Group,Type)%>%
  dplyr::mutate_at(c("0%",   "25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.,caption="HC05, All") %>% kableExtra::kable_classic_2()
```

```{r}
which(casdata$Chem.Group=="Pest" & !(casdata$Type %in% c("H","I","F")))
```



```{r}
casdata%>%filter(class=="Banned_Listed") %>% group_by(class)%>% nest() %>% mutate(n1=map(data,~nrow(.x)))%>%mutate(nsum=map(data,~summaryN(.x$HC05.Chronic)))%>% select(-data)%>% unnest(cols=c(n1,nsum)) %>%
  dplyr::mutate_at(c("0%",   "25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.,caption="HC05, Legacy") %>% kableExtra::kable_classic_2()
```

```{r}
casdata%>%filter(class=="Banned_Listed") %>% group_by(Chem.Group)%>% nest() %>% mutate(n1=map(data,~nrow(.x)))%>%mutate(nsum=map(data,~summaryN(.x$HC05.Chronic)))%>% select(-data)%>% unnest(cols=c(n1,nsum)) %>%arrange(Chem.Group)%>%
  dplyr::mutate_at(c("0%",   "25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.,caption="HC05, Legacy") %>% kableExtra::kable_classic_2()
```

```{r}
casdata%>%filter(class=="Banned_Listed") %>% group_by(Chem.Group,Type)%>% nest() %>% mutate(n1=map(data,~nrow(.x)))%>%mutate(nsum=map(data,~summaryN(.x$HC05.Chronic)))%>% select(-data)%>% unnest(cols=c(n1,nsum))  %>%arrange(Chem.Group,Type)%>%
  dplyr::mutate_at(c("0%",   "25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.,caption="HC05, Legacy") %>% kableExtra::kable_classic_2()
```

```{r}
casdata%>%filter(class=="Current_Use") %>% group_by(class)%>% nest() %>% mutate(n1=map(data,~nrow(.x)))%>%mutate(nsum=map(data,~summaryN(.x$HC05.Chronic)))%>% select(-data)%>% unnest(cols=c(n1,nsum)) %>% ##arrange(Chem.Group)%>%
  dplyr::mutate_at(c("0%",   "25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.,caption="HC05, Current Use") %>% kableExtra::kable_classic_2()
```


```{r}
casdata%>%filter(class=="Current_Use") %>% group_by(Chem.Group)%>% nest() %>% mutate(n1=map(data,~nrow(.x)))%>%mutate(nsum=map(data,~summaryN(.x$HC05.Chronic)))%>% select(-data)%>% unnest(cols=c(n1,nsum)) %>%arrange(Chem.Group)%>%
  dplyr::mutate_at(c("0%",   "25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.,caption="HC05, Current Use") %>% kableExtra::kable_classic_2()
```

```{r}
casdata%>%filter(class=="Current_Use") %>% group_by(Chem.Group,Type)%>% nest() %>% mutate(n1=map(data,~nrow(.x)))%>%mutate(nsum=map(data,~summaryN(.x$HC05.Chronic)))%>% select(-data)%>% unnest(cols=c(n1,nsum)) %>%arrange(Chem.Group,Type)%>%
  dplyr::mutate_at(c("0%",   "25%",  "50%" , "mean", "75%" , "100%"),~as.character(format(.,digits = 3,scientific = T)))%>%
  knitr::kable(.,caption="HC05, Current Use") %>% kableExtra::kable_classic_2()
``` 


```{r fig.width=12}
ggplot(casdata,aes(x=CAS,y=LOQ,col=class))+geom_point()+geom_errorbar(aes(ymin=HC50.Acute,ymax=HC05.Chronic))+scale_y_log10()+ylab("")+theme(axis.text.x = element_text(angle=90),legend.position = "bottom")

```


```{r}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval=F
)
```

## Table 19: Summary statistics of HI and MCR values


```{r}
N.CAS <- sapply(c("Excluded_None","Refined_Metals_PAH","Excluded_Metals","Current_Use"),function(x)getNcas(x,chemclass))%>%as.data.frame(.)
N.CAS$Exclusion.CAS <- rownames(N.CAS)
names(N.CAS)[1] <- "N_Chemical"
```


- Save the intermediate data for whom concerned. 

```{r eval=F}
Res.T1 <- getResData(Data.AggBySiteID.2,chemclass,LOQ.type = c("LOQ.T1"),
            Exclusion.CAS = c("Excluded_None","Refined_Metals_PAH","Excluded_Metals","Current_Use"),Data.SSD.1)
write.csv(Res.T1,file="processed_LOQ.T1.csv")
```


```{r}
Res <- getResData(Data.AggBySiteID.2,chemclass,LOQ.type = c("LOQ.T0"),
            Exclusion.CAS = c("Excluded_None","Refined_Metals_PAH","Excluded_Metals","Current_Use"),Data.SSD.1)

write.csv(Res,file="processed_LOQ.T0.csv")
Res %>% group_by(Exclusion.CAS) %>% summarise(Nsample=n())%>%left_join(N.CAS)%>%knitr::kable(.) %>% kableExtra::kable_classic_2()


```




```{r}
summary2 <- function(x){
  nsum <- quantile(x,c(0,0.25,0.5,0.75,0.9,0.95,1),na.rm = T)
  return(as.data.frame(t(nsum)))
}

```

```{r}
Res %>% group_by(Exclusion.CAS) %>% nest() %>% mutate(nsum=purrr::map(data,~summary2(.x$HI_Chronic)))%>% select(-data)%>% unnest(cols=c(nsum)) %>%#arrange(Chem.Group)%>%
  dplyr::mutate_at(c("0%",   "25%",  "50%" , "50%" , "75%" , "90%",  "95%" , "100%"),~as.character(format(.,digits = 3,scientific = F)))%>%
  knitr::kable(.,caption="HI_Chronic") %>% kableExtra::kable_classic_2()
```


```{r}
Res %>% group_by(Exclusion.CAS) %>% nest() %>% mutate(nsum=purrr::map(data,~summary2(.x$MCR.HC05.Chronic.NOEC)))%>% select(-data)%>% unnest(cols=c(nsum)) %>%#arrange(Chem.Group)%>%
  dplyr::mutate_at(c("0%",   "25%",  "50%" , "50%" , "75%" , "90%",  "95%" , "100%"),~as.character(format(.,digits = 3,scientific = F)))%>%
  knitr::kable(.,caption="MCR.HC05.Chronic.NOEC") %>% kableExtra::kable_classic_2()
```



```{r}
Res %>% group_by(Exclusion.CAS) %>% nest() %>% mutate(nsum=purrr::map(data,~summary2(.x$HI_Acute)))%>% select(-data)%>% unnest(cols=c(nsum)) %>%#arrange(Chem.Group)%>%
  dplyr::mutate_at(c("0%",   "25%",  "50%" , "50%" , "75%" , "90%",  "95%" , "100%"),~as.character(format(.,digits = 3,scientific = F)))%>%
  knitr::kable(.,caption="HI_Acute") %>% kableExtra::kable_classic_2()
```


```{r}
Res %>% group_by(Exclusion.CAS) %>% nest() %>% mutate(nsum=purrr::map(data,~summary2(.x$MCR.HC50.Acute.EC50)))%>% select(-data)%>% unnest(cols=c(nsum)) %>%#arrange(Chem.Group)%>%
  dplyr::mutate_at(c("0%",   "25%",  "50%" , "50%" , "75%" , "90%",  "95%" , "100%"),~as.character(format(.,digits = 3,scientific = F)))%>%
  knitr::kable(.,caption="MCR.HC50.Acute.EC50") %>% kableExtra::kable_classic_2()
```

## Additional Information

### Table 1 for Draft Figures and Tables

```{r}
tmp <- Res[,c("HI_Acute","HI_Chronic","Ndetected","Nmeasured","LOQ.type","Exclusion.CAS")]

tmp <- tmp %>% pivot_longer(cols = c(Ndetected,Nmeasured),names_to="Ntype",values_to="N")

tmp$Ntype<- factor(tmp$Ntype,levels=(c("Nmeasured","Ndetected")))
nsum <- tmp %>% group_by(Exclusion.CAS,LOQ.type,Ntype) %>% nest()%>% dplyr::mutate(nsum=purrr::map(data,~summaryN(.x$N)))%>% dplyr::select(-data)%>% unnest(cols=c(nsum)) %>% mutate(Ntype=factor(Ntype,levels=c("Nmeasured","Ndetected"))) %>% arrange(LOQ.type,Exclusion.CAS,Ntype)

nsum%>%knitr::kable(.,caption="No. of detected and measure Chem") %>% kableExtra::kable_classic_2()
```


```{r}
Res1 <- getResData(Data.AggBySiteID.2,chemclass,LOQ.type = c("LOQ.T0"),
            Exclusion.CAS = c("Metals","PAH","Banned_Listed"),Data.SSD.1)

tmp <- Res1[,c("HI_Acute","HI_Chronic","Ndetected","Nmeasured","LOQ.type","Exclusion.CAS")]
tmp <- tmp %>% pivot_longer(cols = c(Ndetected,Nmeasured),names_to="Ntype",values_to="N")

tmp$Ntype<- factor(tmp$Ntype,levels=(c("Nmeasured","Ndetected")))
nsum <- tmp %>% group_by(Exclusion.CAS,LOQ.type,Ntype) %>% nest()%>% mutate(nsum=map(data,~summaryN(.x$N)))%>% dplyr::select(-data)%>% unnest(cols=c(nsum)) %>% mutate(Ntype=factor(Ntype,levels=c("Nmeasured","Ndetected"))) %>% arrange(LOQ.type,Exclusion.CAS,Ntype)
nsum%>%knitr::kable(.)
```



