---
title: "msPAF"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{msPAF}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval=T,
  fig.width = 12,
  fig.height = 10
)
```


## List of Figures 

- Spatial projections for the distribution of samples in the different CEFIC-MIAT groupings (Group I, Group II, Group IIIA, Group IIIb) for chronic assessment. LOQ.T0 and LOQ.T1 refers to the two assumptions on the contribution of substances below the LOQ.
- Spatial projection of the number of chemicals measured and detected.
- Spatial projections for hazard Index (HI) for the chronic assessment (based on Chronic SSDs HC05s). LOQ.T0 and LOQ.T1 refers to the two assumptions on the contribution of substances below the LOQ. The average of the HI was taken for each monitoring site and is presented in the plots.
- Spatial projections for Maximum Cumulative Ratios (MCRs) for the chronic assessment (based on Chronic SSDs HC05s). LOQ.T0 and LOQ.T1 refers to the two assumptions on the contribution of substances below the LOQ. The average of the HI was taken for each monitoring site and is presented in the plots.


- Graphical Summary
  - Map with LOQ instead of concentrations.
  - Map of the CEFIC-MIAT plot.  

## A bit explanaton why plotting spatial projections.
 
- Spatial bias and substance selection bias?


## Heatmap on the map



```{r}
library(ggplot2)
library(dplyr)
require(maps)
require(viridis)
theme_set(
  theme_void()
  )
library(RColorBrewer)
```



```{r}
## "BA" "BE" "CH" "CY" "CZ" "DE" "ES" "FI" "FR" "HR" "IE" "IT" NA   "LT" "LU" "LV" "NL" "PL" "RO" "RS" "SE"
## "SK" "UK"
#####################################################################
# Some EU Contries
some.eu.countries <- c(
  "Portugal", "Spain", "France", "Switzerland", "Germany",
  "Austria", "Belgium", "UK", "Netherlands",
  "Denmark", "Poland", "Italy", "Cyprus",
  "Croatia", "Slovenia", "Hungary", "Slovakia",
  "Czech republic","Denmark","Finland","Sweden","Bosnia and Herzegovina","Ireland","Lithuania","Luxembourg","Latvia","Poland","Romania","Serbia","Slovakia","Czechia"
)
# Retrievethe map data
some.eu.maps <- map_data("world", region = some.eu.countries)

# Compute the centroid as the mean longitude and lattitude
# Used as label coordinate for country's names
region.lab.data <- some.eu.maps %>%
  group_by(region) %>%
  summarise(long = mean(long), lat = mean(lat))
```


```{r include=F}
cols <- brewer.pal(n = 9, name = 'Paired')
stations1$popup <- with(stations1, paste("<b>", monitoringSiteIdentifier, "</b>"))
#stations1$col <- plyr::mapvalues(stations1$countryCode,from=unique(stations1$countryCode),to=cols)
stations1$lon <- as.numeric(stations1$lon)
stations1$lat <- as.numeric(stations1$lat)
```


```{r}
ggplot(some.eu.maps, aes(x = long, y = lat)) +
  geom_polygon(aes( group = group),fill=NA,col="black",guide=F)+
  scale_fill_viridis_d(option="plasma")+
  theme_void()+
  geom_point(data=stations1%>%filter(LOQ.type=="LOQ.T0" & Exclusion.CAS=="Excluded_None"),aes(x = lon, y = lat,col=log(mean_HI_Acute)),size=0.1)+geom_text(aes(label = region), data = region.lab.data,  size = 3, hjust = 0.5)+scale_color_viridis_c(direction=-1,option = "inferno",name="log(mean HI Acute)")+guides(fill=FALSE,alpha=FALSE)

if(interactive()){
  ggsave("inst/Additional_Figures/map_T0_None.png",width = 8,height=8,dpi=300)
}
```


```{r}

stations1_Mean_tmp <- stations1_Mean %>% mutate(N10=ifelse(mean_N_measured>10,">10","<=10"))
ggplot(data=stations1_Mean_tmp%>%filter(Exclusion.CAS != "Excluded_None"),aes(x = lon, y = lat))+geom_point(aes(col=N10),size=0.1)+  geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+scale_color_manual(values=c("orange","grey"))+guides(fill=FALSE,alpha=FALSE)+facet_grid(LOQ.type~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,30))+ylim(c(35,60))+ guides(colour = guide_legend(override.aes = list(size=10)))#+guides(fill=FALSE,alpha=FALSE,color=guide_legend(override.aes = list(size=6)))##+scale_color_viridis_d(direction=-1,option = "C",name="N measured > 10")

if(interactive()){
  ggsave("inst/Additional_Figures/map_Nmeasured_10.png",width = 15,height=8,dpi=300)
}
```


```{r}

ggplot(data=stations1_Mean%>%filter(Exclusion.CAS != "Excluded_None"& Exclusion.CAS != "Refined_HQ_Metals_PAH"),aes(x = lon, y = lat))+geom_point(aes(col=mean_HI_Chronic),pch=".")+  geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+scale_color_viridis_b(trans="log10",direction=-1,option = "D",name="HI (mean)",breaks=c(1e-04,1e-02,1e+0,1e+02))+guides(fill=FALSE,alpha=FALSE)+facet_grid(LOQ.type~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,30))+ylim(c(35,60))


if(interactive()){
  ggsave("inst/manuscript_maps/map_stations_HI_Chronic_mean_finer.png",width = 10,height=8,dpi=300)
}
ggplot(data=stations1_Mean%>%filter(Exclusion.CAS != "Excluded_None"& Exclusion.CAS != "Refined_HQ_Metals_PAH"),aes(x = lon, y = lat))+geom_point(aes(col=mean_HI_Chronic),size=0.1)+  geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+scale_color_viridis_b(trans="log10",direction=1,option = "D",name="HI (mean)",breaks=c(1e-04,1e-02,1e+0,1e+02))+guides(fill=FALSE,alpha=FALSE)+facet_grid(LOQ.type~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,30))+ylim(c(35,60))


if(interactive()){
  ggsave("inst/manuscript_maps/map_stations_HI_Chronic_mean.png",width = 12,height=8,dpi=300)
  ggsave("inst/manuscript_maps/map_stations_HI_Chronic_mean.pdf",width = 12,height=8)
}



ggplot(data=stations1_Max%>%filter(Exclusion.CAS != "Excluded_None"& Exclusion.CAS != "Refined_HQ_Metals_PAH"),aes(x = lon, y = lat))+geom_point(aes(col=mean_HI_Chronic),size=0.1)+  geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+scale_color_viridis_b(trans="log10",direction=1,option ="D",name="HI (max)",breaks=c(1e-04,1e-02,1e+0,1e+02))+guides(fill=FALSE,alpha=FALSE)+facet_grid(LOQ.type~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,30))+ylim(c(35,60))


if(interactive()){
  ggsave("inst/manuscript_maps/map_stations_HI_Chronic_max.png",width = 12,height=8,dpi=300)
  ggsave("inst/manuscript_maps/map_stations_HI_Chronic_max.pdf",width = 12,height=8)
}
```


```{r}
stdata <- stations1%>%filter(Exclusion.CAS != "Excluded_None" & Exclusion.CAS != "Refined_HQ_Metals_PAH" & LOQ.type=="LOQ.T0") %>% pivot_longer(cols=c(mean_N_measured,mean_N_detected),names_to="Ntype",values_to="N")
stdata$Ntype <- factor(stdata$Ntype,levels=c("mean_N_measured","mean_N_detected"))
stdata$Exclusion.CAS <- factor(stdata$Exclusion.CAS,levels=c("Excluded_Metals","Banned_Listed","Current_Use"))
ggplot(stdata,aes(x = lon, y = lat))+geom_point(aes(col=N),size=0.1)+  geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) + theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+scale_color_viridis_c(trans="log10",direction=-1,option = "D")+guides(fill=FALSE,alpha=FALSE)+facet_grid(Ntype~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,30))+ylim(c(35,60))


if(interactive()){
  ggsave("inst/manuscript_maps/map_mean_N_measure.png",width=12,height=8,dpi=300)
  ggsave("inst/manuscript_maps/map_mean_N_measure.pdf",width=12,height=8)
}
```


```{r}
ggplot(data=stations1_Max%>%filter(Exclusion.CAS != "Excluded_None"& Exclusion.CAS != "Refined_HQ_Metals_PAH"),aes(x = lon, y = lat))+geom_point(aes(col=mean_MCR_Chronic),size=0.1)+geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+scale_color_viridis_c(direction=1,option = "D",name="MCR (max)")+guides(fill=FALSE,alpha=FALSE)+facet_grid(LOQ.type~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,30))+ylim(c(35,60))

if(interactive()){
  ggsave("inst/manuscript_maps/map_MCR_Chronic_Max.png",width=12,height=8,dpi=300)
  ggsave("inst/manuscript_maps/map_MCR_Chronic_Max.pdf",width=12,height=8)
  
}
```


```{r}
ggplot(data=stations1_Mean%>%filter(Exclusion.CAS != "Excluded_None"& Exclusion.CAS != "Refined_HQ_Metals_PAH"),aes(x = lon, y = lat))+geom_point(aes(col=mean_MCR_Chronic),size=0.1)+geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+scale_color_viridis_c(direction=1,option = "D",name="MCR (mean)")+guides(fill=FALSE,alpha=FALSE)+facet_grid(LOQ.type~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,30))+ylim(c(35,60))


if(interactive()){
  ggsave("inst/manuscript_maps/map_MCR_Chronic_Mean.png",width=12,height=8,dpi=300)
  ggsave("inst/manuscript_maps/map_MCR_Chronic_Mean.pdf",width=12,height=8)
}
```


```{r}
ggplot(data=stations1_Max%>%filter(Exclusion.CAS != "Excluded_None"& Exclusion.CAS != "Refined_HQ_Metals_PAH"),aes(x = lon, y = lat))+geom_point(aes(col=(Group_AF1_Chronic)),size=0.1)+geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+scale_color_viridis_d(direction=-1,option = "D",name="Group (max)")+guides(fill=FALSE,alpha=FALSE,color=guide_legend(override.aes = list(size=2)))+facet_grid(LOQ.type~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,30))+ylim(c(35,60))



if(interactive()){
  ggsave("inst/manuscript_maps/map_Group_AF1_Chronic_Max.png",width=12,height=8,dpi=300)
  ggsave("inst/manuscript_maps/map_Group_AF1_Chronic_Max.pdf",width=12,height=8)
}
```


```{r}
ggplot(data=stations1_Mean%>%filter(Exclusion.CAS != "Excluded_None"& Exclusion.CAS != "Refined_HQ_Metals_PAH"),aes(x = lon, y = lat))+geom_point(aes(col=(Group_AF1_Chronic)),size=0.1)+  geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+scale_color_viridis_d(direction=1,option = "D",name="Group (mean)")+guides(fill=FALSE,alpha=FALSE,color=guide_legend(override.aes = list(size=2)))+facet_grid(LOQ.type~Exclusion.CAS)+labs(x="",y="")+xlim(c(-11,30))+ylim(c(35,60))


if(interactive()){
  ggsave("inst/manuscript_maps/map_Group_AF1_Chronic_Mean.png",width=12,height=8,dpi=300)
  ggsave("inst/manuscript_maps/map_Group_AF1_Chronic_Mean.pdf",width=12,height=8)
}
```





## Graphic Abstract


```{r}
Res_Max_driver5 <- getResData(Data.AggBySiteID.2,chemclass,LOQ.type = c("LOQ.T0","LOQ.T1"),
                              Exclusion.CAS = c("Excluded_None","Refined_HQ_Metals_PAH","Excluded_Metals","Current_Use"),
                              exclude.substances= driver5,Data.SSD.1,useAllMax=T)
Res_Mean_driver5 <- getResData(Data.AggBySiteID.2,chemclass,LOQ.type = c("LOQ.T0","LOQ.T1"),
                               Exclusion.CAS = c("Excluded_None","Refined_HQ_Metals_PAH","Excluded_Metals","Current_Use"),exclude.substances= driver5,Data.SSD.1,useAllMean=T)

stations1_Mean_driver5 <- Res_Mean_driver5 %>% group_by(LOQ.type,Exclusion.CAS,monitoringSiteIdentifier) %>%
  summarize(mean_HQ_Max_Acute=mean(HQ_Max_Acute,na.rm=T),mean_HQ_Max_Chronic=mean(HQ_Max_Chronic,na.rm=T),mean_HI_Acute=mean(HI_Acute,na.rm=T),mean_HI_Chronic=mean(HI_Chronic,na.rm=T),
            mean_N_measured=mean(Nmeasured,na.rm=T),mean_N_detected=mean(Ndetected,na.rm=T),mean_MCR_Chronic=mean(MCR.HC05.Chronic.NOEC,na.rm=T),mean_MCR_Acute=mean(MCR.HC50.Acute.EC50,na.rm=T))%>%
   mutate(Group_AF1_Chronic=get_group(HI=mean_HI_Chronic,HQ=mean_HQ_Max_Chronic,MCR=mean_MCR_Chronic,AF=1)) %>%
  mutate(Group_AF1_Acute=get_group(HI=mean_HI_Acute,HQ=mean_HQ_Max_Acute,MCR=mean_MCR_Acute,AF=1))


stations1_Max_driver5 <- Res_Max_driver5 %>% group_by(LOQ.type,Exclusion.CAS,monitoringSiteIdentifier) %>%
  summarize(mean_HQ_Max_Acute=mean(HQ_Max_Acute,na.rm=T),mean_HQ_Max_Chronic=mean(HQ_Max_Chronic,na.rm=T),mean_HI_Acute=mean(HI_Acute,na.rm=T),mean_HI_Chronic=mean(HI_Chronic,na.rm=T),
            mean_N_measured=mean(Nmeasured,na.rm=T),mean_N_detected=mean(Ndetected,na.rm=T),mean_MCR_Chronic=mean(MCR.HC05.Chronic.NOEC,na.rm=T),mean_MCR_Acute=mean(MCR.HC50.Acute.EC50,na.rm=T))%>%
  mutate(Group_AF1_Chronic=get_group(HI=mean_HI_Chronic,HQ=mean_HQ_Max_Chronic,MCR=mean_MCR_Chronic,AF=1)) %>%
  mutate(Group_AF1_Acute=get_group(HI=mean_HI_Acute,HQ=mean_HQ_Max_Acute,MCR=mean_MCR_Acute,AF=1))
stations1_Mean_driver5 <- left_join(stations1_Mean_driver5,stations)
stations1_Max_driver5 <- left_join(stations1_Max_driver5,stations)

stations1_Mean_driver5$Exclusion.CAS <- factor(stations1_Mean_driver5$Exclusion.CAS,levels=c("Excluded_None","Refined_HQ_Metals_PAH","Excluded_Metals","Banned_Listed","Current_Use"))
stations1_Max_driver5$Exclusion.CAS <- factor(stations1_Max_driver5$Exclusion.CAS,levels=c("Excluded_None","Refined_HQ_Metals_PAH","Excluded_Metals","Banned_Listed","Current_Use"))

s1<- stations1_Mean_driver5 %>% filter(LOQ.type=="LOQ.T0",Exclusion.CAS=="Excluded_Metals")%>% mutate(used="Mean",facet="Excluding >5% drivers")
s2<- stations1_Mean%>% filter(LOQ.type=="LOQ.T0",Exclusion.CAS=="Excluded_Metals")%>% mutate(used="Mean",facet="Excluded_Metals")
s3<- stations1_Max_driver5 %>% filter(LOQ.type=="LOQ.T0",Exclusion.CAS=="Excluded_Metals")%>% mutate(used="Max",facet="Excluding >5% drivers")
s4<- stations1_Max%>% filter(LOQ.type=="LOQ.T0",Exclusion.CAS=="Excluded_Metals")%>% mutate(used="Max",facet="Excluded_Metals")
sdata <- rbind(s1,s2,s3,s4)
sdata$used <- factor(sdata$used,levels=c("Mean","Max"))
```


```{r}
ggplot(data=sdata,aes(x = lon, y = lat))+geom_point(aes(col=mean_HI_Chronic),size=0.1)+geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+scale_color_viridis_c(trans="log10",direction=1,option = "D",name="HI",breaks=c(1e-6,1e-4,1e-2,1e+0,1e+2))+guides(fill=FALSE,alpha=FALSE)+facet_grid(used~facet)+labs(x="",y="")+xlim(c(-11,30))+ylim(c(35,60))

if(interactive()){
  ggsave("inst/manuscript_maps/map_HI_mean_max.png",width=10,height=8,dpi=300)
  ggsave("inst/manuscript_maps/map_HI_mean_max.pdf",width=10,height=8)
}
```



```{r}
sdata <- sdata %>% mutate(HI_1=ifelse(mean_HI_Chronic>1,"HI>1","HI<=1"))
ggplot(data=sdata,aes(x = lon, y = lat))+geom_point(aes(col=factor(HI_1)),size=0.1)+geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+guides(fill=FALSE,alpha=FALSE,color=guide_legend(override.aes = list(size=2)))+facet_grid(used~facet)+labs(x="",y="")+xlim(c(-11,30))+ylim(c(35,60))+scale_color_manual(values=c("darkgreen","red"),name="HI")#+scale_color_viridis_d(direction=1,option = "D",name="HI")

if(interactive()){
  ggsave("inst/manuscript_maps/map_HI_1_mean_max.png",width=10,height=8,dpi=300)
  ggsave("inst/manuscript_maps/map_HI_1_mean_max.pdf",width=10,height=8)
}

sdata%>%group_by(LOQ.type,facet,used) %>% summarise(p=sum(mean_HI_Chronic>1)/n())

```



```{r}
theme_set(theme_bw())
ggplot(data=sdata,aes(x = lon, y = lat))+geom_point(aes(col=factor(HI_1)),size=0.1)+geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+geom_text(aes(x=long,y=lat,label = region), data = region.lab.data,  size = 3, hjust = 0.5)+guides(fill=FALSE,alpha=FALSE,color=guide_legend(override.aes = list(size=2)))+facet_grid(used~facet)+labs(x="",y="")+xlim(c(-11,30))+ylim(c(35,60))+scale_color_manual(values=c("darkgreen","red"),name="HI")+theme(panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank())
if(interactive()){
  ggsave("inst/manuscript_maps/graphic_abstract.png",width=10,height=8,dpi=300)
  ggsave("inst/manuscript_maps/graphic_abstract.pdf",width=10,height=8)
}


ggplot(data=sdata,aes(x = lon, y = lat))+geom_point(aes(col=factor(HI_1)),size=0.1)+geom_polygon(data=some.eu.maps, aes(x = long, y = lat,group=group),fill=NA,color="black",guide=F) +  theme_bw()+guides(fill=FALSE,alpha=FALSE,color=guide_legend(override.aes = list(size=2)))+facet_grid(used~facet)+labs(x="",y="")+xlim(c(-11,30))+ylim(c(35,60))+scale_color_manual(values=c("darkgreen","red"),name="HI")+theme(panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.background = element_blank())
if(interactive()){
  ggsave("inst/manuscript_maps/graphic_abstract_nolabel.png",width=10,height=8,dpi=300)
  ggsave("inst/manuscript_maps/graphic_abstract_nolabel.pdf",width=10,height=8)
}

```

